### 2011-11-02 docs/src/currydoc.tex
CurryDoc and comments improved

The documentation comment for the module (i.e., the documentation
comment at the beginning of the module before the module header)
can be formatted with
\href{http://en.wikipedia.org/wiki/Markdown}{Markdown's syntax}\index{markdown}
provided that the
\href{http://johnmacfarlane.net/pandoc/}{pandoc}\index{pandoc}
 tool is installed.
Other documentations comments, like comments for operations
or data types, can contain Markdown annotations for
emphasizing elements (e.g., \verb!*emph*! or \verb!_verb_!),
strong elements (e.g., \verb!**important**! or \verb!__important__!),
or code elements (e.g., \verb!`3+4`!).
If \code{pandoc} is not installed, one should run CurryDoc
with the parameter \ccode{--nomarkdown}.

@@

--- The function conc concatenates two lists.
--- @param xs - the first list
--- @param ys - the second list
--- @return a list containing all elements of xs and ys
conc []     ys = ys
conc (x:xs) ys = x : conc xs ys
-- this comment will not be included in the documentation

--- The function last computes the last element of a given list.
--- @param xs - the given input list
--- @return last element of the input list
last xs | conc ys [x] =:= xs  = x   where x,ys free

--- This data type defines polymorphic trees.
--- @cons Leaf - a leaf of the tree
--- @cons Node - an inner node of the tree
data Tree a = Leaf a | Node [Tree a]
\end{verbatim}
}
\noindent
To generate the documentation, execute the command\pindex{currydoc}
\startprog
currydoc --html Example
\stopprog
(\code{currydoc} is a command usually stored in \code{$kics2home$/bin}
where $kics2home$ is the installation directory of KiCS2;
see Section~\ref{sec-general}).
This command creates the directory \code{DOC_Example} (if it does not exist)
and puts all HTML documentation files for the main program module
\code{Example}
and all its imported modules in this directory together with
a main index file \code{index.html}.
If one prefers another directory for the documentation files,
one can also execute the command
\startprog
currydoc --html docdir Example
\stopprog
where \code{docdir} is the directory for the documentation files.

>>>>

The documentation comment for the module (i.e., the documentation
comment at the beginning of the module before the module header)
can be formatted with a subset of
\href{http://en.wikipedia.org/wiki/Markdown}{Markdown's syntax}\index{markdown}.
For instance, it can contain Markdown annotations for
emphasizing elements (e.g., \verb!*emph*! or \verb!_verb_!),
strong elements (e.g., \verb!**important**! or \verb!__important__!),
code elements (e.g., \verb!`3+4`!), code blocks (lines prefixed by four blanks),
unordered lists (lines prefixed by two blanks followed by ``\verb!* !''),
ordered lists (lines prefixed by two blanks followed by a digit and a dot),
quotations (lines prefixed by ``\verb!> !''),
and web links of the form \ccode{<http://\ldots>}
or \ccode{[link text](http://\ldots)}.
If the Markdown syntax should not be used, one could run CurryDoc
with the parameter \ccode{--nomarkdown}.

@@

--- The function `conc` concatenates two lists.
--- @param xs - the first list
--- @param ys - the second list
--- @return a list containing all elements of `xs` and `ys`
conc []     ys = ys
conc (x:xs) ys = x : conc xs ys
-- this comment will not be included in the documentation

--- The function `last` computes the last element of a given list.
--- @param xs - the given input list
--- @return last element of the input list
last xs | conc ys [x] =:= xs  = x   where x,ys free

--- This data type defines _polymorphic_ trees.
--- @cons Leaf - a leaf of the tree
--- @cons Node - an inner node of the tree
data Tree a = Leaf a | Node [Tree a]
\end{verbatim}
}
\noindent
To generate the documentation, execute the command\pindex{currydoc}
\startprog
currydoc --html Example
\stopprog
(\code{currydoc} is a command usually stored in \code{$kics2home$/bin}
where $kics2home$ is the installation directory of KiCS2;
see Section~\ref{sec-general}).
This command creates the directory \code{DOC_Example} (if it does not exist)
and puts all HTML documentation files for the main program module
\code{Example}
and all its imported modules in this directory together with
a main index file \code{index.html}.
If one prefers another directory for the documentation files,
one can also execute the command
\startprog
currydoc --html docdir Example
\stopprog
where \code{docdir} is the directory for the documentation files.
